Project1_RM

### 2020-02-11 Project1_RM.Rmd
Update Project1_RM.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(geosphere)

options(scipen=999)
```

```{r}
knitr::opts_chunk$set(echo = TRUE)
airbnb <-read.csv(file="/Users/reagan/Documents/_SMU/Spring_2020/Applied_Statistics/Applied_Stats_Project/Project_1/AB_NYC_2019.csv",header=TRUE)

@@

```{r}
fit <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
summary(fit)
plot(fit)
```

>>>>

Loading libraries and settings
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(geosphere)
options(scipen=999)
options(max.print=1000000)
```

Exploratory Data Analysis
```{r}
knitr::opts_chunk$set(echo = TRUE)
#MAC
#airbnb <- read.csv(file="/Users/reagan/Documents/_SMU/Spring_2020/Applied_Statistics/Applied_Stats_Project/Project_1/AB_NYC_2019.csv",header=TRUE)

#PC
airbnb <- read.csv(file="C:/Users/EREAMEA/Documents/_SMU/Applied Statistics/Semester Project/AB_NYC_2019.csv",header=TRUE)

@@

Full data set regression fit with interaction term, no transformation
```{r}
fit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
summary(fit)
plot(fit)
```

Full data set regression fit with interaction term, log - linear transformation
```{r}
fit_log <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = airbnb)
summary(fit_log)
plot(fit_log)
```

Entire home/apt data set regression fit, log - linear transformation
```{r}
fit_EH <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
summary(fit_EH)
plot(fit_EH)
```

Private room data set regression fit, log - linear transformation
```{r}
fit_PR <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
summary(fit_EH)
plot(fit_PR)
```

Shared room data set regression fit, log - linear transformation
```{r}
fit_SR <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood, data = airbnb_EH)
summary(fit_SR)
plot(fit_SR)
```
